### 2024-12-02 README.Rmd
change package name

# embeddingplyr: Tools for Working With Text Embeddings

@@

embeddingplyr enables common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). It includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. [GloVe](https://nlp.stanford.edu/projects/glove/)), applying them to words, aggregating to produce text embeddings, reducing dimensionality, and more.

@@

You can install the development version of embeddingplyr from [GitHub](https://github.com/) with:

``` r
# devtools package required to install quanteda from Github 
remotes::install_github("rimonim/embeddingplyr") 
```

@@

embeddingplyr is designed to facilitate the use of word and text embeddings in common data manipulation and text analysis workflows, without introducing new syntax or unfamiliar data structures.

embeddingplyr is model agnostic; it can be used to work with embeddings from decontextualized models like [GloVe](https://nlp.stanford.edu/projects/glove/) and [word2vec](https://code.google.com/archive/p/word2vec/), or from contextualized models like BERT or others made available through the '[text](https://r-text.org)' package.

@@

embeddingplyr won't help you train new embedding models, but it can load embeddings from a file or download them from online. This is especially useful for pretrained word embedding models like GloVe, word2vec, and fastText. Dozens of these models can be conveniently downloaded from online sources with `load_embeddings()`.

```{r, warning=FALSE, message=FALSE}
library(embeddingplyr)

>>>>

# embedplyr: Tools for Working With Text Embeddings

@@

embedplyr enables common operations with word and text embeddings within a 'tidyverse'/'quanteda' workflow, as demonstrated in [Data Science for Psychology: Natural Language](http://ds4psych.com). It includes simple functions for calculating common similarity metrics, as well as higher level functions for loading pretrained word embedding models (e.g. [GloVe](https://nlp.stanford.edu/projects/glove/)), applying them to words, aggregating to produce text embeddings, reducing dimensionality, and more.

@@

You can install the development version of embedplyr from [GitHub](https://github.com/) with:

``` r
# devtools package required to install quanteda from Github 
remotes::install_github("rimonim/embedplyr") 
```

@@

embedplyr is designed to facilitate the use of word and text embeddings in common data manipulation and text analysis workflows, without introducing new syntax or unfamiliar data structures.

embedplyr is model agnostic; it can be used to work with embeddings from decontextualized models like [GloVe](https://nlp.stanford.edu/projects/glove/) and [word2vec](https://code.google.com/archive/p/word2vec/), or from contextualized models like BERT or others made available through the '[text](https://r-text.org)' package.

@@

embedplyr won't help you train new embedding models, but it can load embeddings from a file or download them from online. This is especially useful for pretrained word embedding models like GloVe, word2vec, and fastText. Dozens of these models can be conveniently downloaded from online sources with `load_embeddings()`.

```{r, warning=FALSE, message=FALSE}
library(embedplyr)
